---
title: "DSC for linear regression: usage instructions"
author: "Peter Carbonetto, Gao Wang and Matthew Stephens"
date: April 9, 2019
site: workflowr::wflow_site
output: workflowr::wflow_html
---

Please follow these steps to start using the linear regression DSC.

## Installing the software and R packages

First, install [DSC][dsc].

Next, install [R][R], as well as the R packages used. The devtools and
glmnet packages can be installed from CRAN:

```{r, eval=FALSE}
install.packages("devtools")
install.packages("glmnet")
install.packages("ggplot2")
install.packages("cowplot")
```

The susieR, varbvs and dscrutils packages can be installed from GitHub
using [devtools][devtools]:

```{r, eval=FALSE}
library(devtools)
install_github("stephenslab/susieR")
install_github("pcarbo/varbvs",subdir = "varbvs-R")
install_github("stephenslab/dsc",subdir = "dscrutils")
```

Finally, clone or download this git repository.

## Running the DSC

Now you should have everything you need to run the DSC. Navigate to
the "dsc" directory inside your local copy of the git repository, and
run it with this command (here we have chosen 4 threads, but you may
want to adjust the number of threads to better suit your computer):

```bash
dsc -c 4 linreg.dsc
```

Go grab a coffee while you wait for the DSC to run. It may take some
time, perhaps as long as 30 minutes, for all the DSC pipelines to
complete.

## Exploring the DSC results

Once the DSC has finished running, you may want to work through [this
short analysis](results_overview.html) to explore the results of the
DSC in R or RStudio. When running the R code, make sure your working
directory is set to the "analysis" directory in the git repository.

## Creating the workflowr site

To recreate and commit the website from the R Markdown files, this can
be done using the "wflow_publish" function from the
[workflowr][workflowr] package, after setting your working directory
to the "analysis" directory:

```{r, eval=FALSE}
library(workflowr)
wflow_publish("index.Rmd")
wflow_publish("usage_instructions.Rmd")
wflow_publish("results_overview.Rmd")
```

These lines of R code will populate the "docs" directory with the
newly rendered webpages, and commit the changes to the git repository.

## Note

*DSC is specifically designed to be extended*—please make improvements
to this DSC by modifying our experiments, or by adding new methods,
data scenarios or evaluation metrics.

[dsc]:       https://github.com/stephenslab/dsc
[R]:         https://www.r-project.org
[devtools]:  https://github.com/r-lib/devtools
[workflowr]: https://github.com/jdblischak/workflowr
